### 2013-09-12 thesis/src/chapters/chapter-3.tex
added 2 more data analysis modesl

\section{Data analysis}
Having policies defined, their conditions are evaluated against data aquired from sensors. In a simplest case this evaluation can be based on a Threshold Model \cite{LiWoZh05}, which defines a valid range. In cases when given metric violates that condition (i.e. value is either smaller than minimal or bigger than maximal acceptable) corresponding resource is properly adjusted. While trivial in its form, cases of AWS, OpenShift, Carina, OneCloud proves it is useful in a real-world scenarios. Having that said, more sophisticated algorithms also exists:
\begin{itemize}
  \item \textit{integer programming} - autoscaling is reduced to server interger programming problems, which aims to minimize the cost or maximize the computing power with either computing power constraints or
budget constraints \cite{MaLiHu10}
  \item \textit{prediction error correction} - \cite{ShSuGuWi11}
\end{itemize}

>>>>

\section{Data analysis}
Having policies defined, their conditions are evaluated against data aquired from sensors. In a simplest case this evaluation can be based on a Threshold Model \cite{LiWoZh05}, which defines a valid range. In cases when given metric violates that condition (i.e. value is either smaller than minimal or bigger than maximal acceptable) corresponding resource is properly adjusted. While trivial in its form, cases of AWS, OpenShift, Carina, OneCloud proves it is useful in a real-world scenarios. Having that said, more sophisticated algorithms also exists:
\begin{itemize}
  \item \textit{integer programming} - autoscaling is reduced to server interger programming problems, which aims to minimize the cost or maximize the computing power with either computing power constraints or
budget constraints \cite{MaLiHu10}
  \item \textit{prediction error correction} - \cite{ShSuGuWi11}
  \item \textit{linearized dynamic control} - linearized correction model is based on control equations \cite{AbShBh02}:

    \begin{equation}
      x(k+1)=Ax(k)+Bu(k)
    \end{equation}

    \begin{equation}
       y(k) = C x(k) + D u(k) + E z(k)
    \end{equation}
    where x denotes the state variable vector and coefficient matrices: A B C D E are fitted to historical data as a regression model - \cite{DiLuFrHePa03}

  \item \textit{markov decision process model} - computes optimal reaction to state changes by using obsercation on the system with assumptions about the rate of changes expected in the future \cite{AbWo02}
\end{itemize}
